\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-14 paper/main.tex
fixed remaining comments

\textbf{Test Oracles.}~
The bug reproduction code includes python tests (pytest). The test
oracle is satisfied when the bug is reproduced successfully. For bugs
that throw an unexpected exception, the test catches the exception and
reports the exception details along with a pass status. For bugs that
result in incorrect output value, assertions are placed in the code to
expect the incorrect output value, hence passing the test when the bug
occurs. For bugs that crash after raising a signal, the code snippet
is placed in a seperate file and executed, while the file contaning
the actual test asserts the presence of the signal raised by the
code. Upon successful reproduction, the original code crashes raising
the proper signal and the assertion passes.\Fix{Please review and
  revise}

@@

Let us use the bug 120903~\Fix{cite} from \torch\ to demonstrate the
command \CodeIn{run-test}, which runs a test to reproduce a bug on an
environment with the necessary dependencies installed. Use the
following command to reproduce the bug:

>>>>

\textbf{Test Oracles.}~
The bug reproduction code includes python tests (pytest). The test
oracle is satisfied when the bug is reproduced successfully. For bugs
that throw an unexpected exception, the test catches the exception and
reports the exception details along with a pass status. For bugs that
result in incorrect output value, assertions are placed in the code to
expect the incorrect output value, hence passing the test when the bug
occurs. For bugs that crash after raising a signal, the code snippet
is placed in a seperate file and executed, while the file contaning
the actual test asserts the presence of the signal raised by the
code. Upon successful reproduction, the original code crashes raising
the proper signal and the assertion passes.
% \Fix{Please review and revise}

@@

Let us use the bug 120903~\cite{torch120903} from \torch\ to demonstrate the
command \CodeIn{run-test}, which runs a test to reproduce a bug on an
environment with the necessary dependencies installed. Use the
following command to reproduce the bug:
